NumPy---Array Computation for Python

### 2019-12-17 paper.tex
Move funding to intro

@@

\subsection*{Current status (maturity, users)}

\subsection*{Enabled ecosystem }

@@

@@

Historically, NumPy was developed primarily by voluteers in their free time.
% some funding at Berkeley, the documentation project, Travis funding ...
Over the last few years, there has an increase in paid full-time developers due
to new sources of funding.

\subsection*{Maintainer overview}

@@

\subsection*{Industry collaboration}

>>>>

For many years, NumPy operated without external funding, development
time mostly being contributed freely by students and researchers in
their spare time.  In-person meetings were sponsored off of
individual's research grants, and while industry sponsored
contributions were made, notably those by Mark Wiebe when he was
sponsored by Travis Oliphant at Continuum Analytics, mostly the package had rapid growth
and adoption without external investment.

% In 2014, NumPy received its
% first large grants from the Moore and Sloan foundations, totaling 1.3M
% dollars.  This allowed for hiring several full time programmers and,
% with the support of community members, mobilized a project that had
% become stagnant for the several years prior.

\subsection*{Current status}

NumPy is now actively developed, with weekly online developer
meetings, a formalized NumPy enhancement proposal process, and
multiple active grants (but still almost no industry support).
% check almost no industry

% (maturity, users)

@@

% https://numpy.org/neps/scope.html

@@

% https://numpy.org/neps/roadmap.html

@@

@@

% may be useful:
% - https://github.com/docathon/watchtower
% - https://github.com/machine-shop/oss_devkit/blob/master/plot_pr.py % (PR over time plot, there may be other better versions out there)
